---
title: 'ADLP: Accident and Development period adjusted Linear Pools'
output:
  html_document:
    df_print: paged
vignette: |
  %\VignetteIndexEntry{ADLP: Accident and Development period adjusted Linear Pools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
 )

```

This vignette aims to illustrate how the `ADLP` package can be used to objectively
combine multiple stochastic loss reserving models such that the strengths offered 
by different models can be utilised effectively.

Set Up
---

To showcase the `ADLP` package, we will import a test claims dataset from
[`SynthETIC`](https://CRAN.R-project.org/package=SynthETIC). Note 
that some data manipulation is needed to transform the imported object into 
a compatible format for `ADLP`, however any `data.frame` with column 1 titled 
"origin" for accident periods and column 2 titled "dev" for development periods
will work. All other columns can be constructed as required for model inputs.

```{r setup}
library(ADLP)
if (!require(SynthETIC)) install.packages("SynthETIC")
if (!require(tidyverse)) install.packages("tidyverse")
library(tidyverse)

# Import dummy claims dataset
claims_dataset <- claims_dataset <- ADLP::test_claims_dataset

head(claims_dataset)
```

Training and Validation Split
---

As the ADLP weightings are determined through testing on a validation set,
we need to split the claims dataset into a training, validation and testing set.

```{r}

# Included train/validation splitting function
train_val <- ADLP::train_val_split_method1(
    df = claims_dataset,
    tri.size = 40,
    val_ratio = 0.3,
    test = TRUE
)

train_data <- train_val$train
valid_data <- train_val$valid
insample_data <- rbind(train_data, valid_data)
test_data <- train_val$test

print("Number of observations in each row")
print(nrow(train_data))
print(nrow(valid_data))
print(nrow(test_data))

print("Approximation for val_ratio")
print(nrow(valid_data)/(nrow(insample_data)))

```

Constructing Components
---

This example will construct an ADLP with three components. However, any number of
base models will also function well. 

While we use `glm` style models in this example, the only requirement for the 
base models is support for the S3 method 'formula', and being able to be fitted
on by the datasets of similar structure to `claims_dataset`. To demonstrate the veModels from the
[`gamlss`](https://CRAN.R-project.org/package=gamlss) package 
was used while proofing the `ADLP` concept.

```{r}
base_model1 <- glm(formula = claims~factor(dev),
                   family=gaussian(link = "identity"), data=train_data)

tau <- 1e-8
base_model2 <- glm(formula = (claims+tau)~calendar,
                   family=Gamma(link="inverse"), data=train_data)

base_model3 <- glm(formula = claims~factor(origin),
                   family=gaussian(link = "identity"), data=train_data)

base_model1_full <- update(base_model1, data = insample_data)
base_model2_full <- update(base_model2, data = insample_data)
base_model3_full <- update(base_model3, data = insample_data)
```

To also support desired outputs including densities and predictions, the base
components will also require `calc_dens`, `calc_mu`, `calc_cdf` and `sim_fun`
methods to be defined for each base component. See `?adlp_component` for more
information.

```{r}
################################################################################
# Normal distribution densities and functions
dens_normal <- function(y, model, newdata){
    pred_model <- predict(model, newdata=newdata, type="response", se.fit=TRUE)
    mu <- pred_model$fit
    sigma <- pred_model$residual.scale
    return(dnorm(x=y, mean=mu, sd=sigma))
}

cdf_normal<-function(y, model, newdata){
    pred_model <- predict(model, newdata=newdata, type="response", se.fit=TRUE)
    mu <- pred_model$fit
    sigma <- pred_model$residual.scale
    return(pnorm(q=y, mean=mu, sd=sigma))
}

mu_normal<-function(model, newdata){
    mu <- predict(model, newdata=newdata, type="response")
    mu <- pmax(mu, 0)
    return(mu)
}

sim_normal<-function(model, newdata){
    pred_model <- predict(model, newdata=newdata, type="response", se.fit=TRUE)
    mu <- pred_model$fit
    sigma <- pred_model$residual.scale
    
    sim <- rnorm(length(mu), mean=mu, sd=sigma)
    sim <- pmax(sim, 0)
    return(sim)
}

################################################################################
# Gamma distribution densities and functions
dens_gamma <- function(y, model, newdata){
    pred_model <- predict(model, newdata=newdata, type="response", se.fit=TRUE)
    mu <- pred_model$fit
    sigma <- pred_model$residual.scale
    return(dgamma(x=y, shape = 1/sigma, scale=(mu*sigma)^2))
}

cdf_gamma <- function(y, model, newdata){
    pred_model <- predict(model, newdata=newdata, type="response", se.fit=TRUE)
    mu <- pred_model$fit
    sigma <- pred_model$residual.scale
    return(pgamma(q=y, shape = 1/sigma, scale=(mu*sigma)^2))
}

mu_gamma <- function(model, newdata, tau){
    mu <- predict(model, newdata=newdata, type="response")
    mu <- pmax(mu - tau, 0)
    return(mu)
}

sim_gamma <- function(model, newdata, tau){
    pred_model <- predict(model, newdata=newdata, type="response", se.fit=TRUE)
    mu <- pred_model$fit
    sigma <- pred_model$residual.scale
    
    sim <- rgamma(length(mu), shape = 1/sigma, scale=(mu*sigma)^2)
    sim <- pmax(sim - tau, 0)
    return(sim)
}

```

Fitting ADLPs
---

The different user defined base models are then structured as a `adlp_component`
object to be used in model fitting for `adlp`.

```{r}
# Constructing ADLP component classes

base_component1 = adlp_component(
    model_train = base_model1, 
    model_full = base_model1_full, 
    calc_dens = dens_normal,
    calc_cdf = cdf_normal,
    calc_mu = mu_normal,
    sim_fun = sim_normal
)

base_component2 = adlp_component(
    model_train = base_model2, 
    model_full = base_model2_full, 
    calc_dens = dens_gamma,
    calc_cdf = cdf_gamma,
    calc_mu = mu_gamma,
    sim_fun = sim_gamma,
    tau = tau
)

base_component3 = adlp_component(
    model_train = base_model3, 
    model_full = base_model3_full, 
    calc_dens = dens_normal,
    calc_cdf = cdf_normal,
    calc_mu = mu_normal,
    sim_fun = sim_normal
)

components <- adlp_components(
    base1 = base_component1,
    base2 = base_component2,
    base3 = base_component3
)

```

`adlp` objects are fitted using the validation data to determine the best
weighting to choose for each partition. 

Note that different partitions can be used. `fit1` uses no partition, meaning
that the weights are determined via standard linear pooling. `fit2` is an example
of creating 3 partitions in the validation data, with the accident periods being
chosen to optimise the desired weighting of each partition.


```{r, error = T}
# Fitting ADLP class
fit1 <- adlp(
    components_lst = components,
    newdata = valid_data,
    partition_func = ADLP::adlp_partition_none
)

fit2 <- adlp(
    components_lst = components,
    newdata = valid_data,
    partition_func = ADLP::adlp_partition_ap,
    tri.size = 40,
    size = 3,
    weights = c(3, 1, 2)
)


fit1
fit2
```

Supported Outputs
---

The `ADLP` package supports calculation of log score, CRPS, prediction and 
simulation from each of the ensemble models. Note that the user-defined functions
for each of the component models is necessary to perform this calculation.

```{r}
# Log Score
ensemble_logS <- adlp_logS(fit1, test_data, model = "full")

# Cumulative Ranked Probability Score
ensemble_CRPS <- adlp_CRPS(fit1, test_data, response_name = "claims", model = "full", sample_n = 1000)

# Predictions
ensemble_means <- predict(fit1, test_data)

# Simulations
ensemble_simulate <- adlp_simulate(100, fit1, test_data)

boxplot(ensemble_logS$dens_val, main = "Log Score")
boxplot(ensemble_CRPS$ensemble_crps, main = "Cumulative Ranked Probability Score")
boxplot(ensemble_means$ensemble_mu, main = "Predictions")
boxplot(ensemble_simulate$simulation, main = "Simulations")
```


Different partition
---

The sample below shows how a user can define their own partition function to be
used within model fitting.

```{r}
# Defining own partition function
user_defined_partition <- function(df) {
    return (list(
        subset1 = df[(as.numeric(as.character(df$origin)) >= 1) & (as.numeric(as.character(df$origin)) <= 15), ],
        subset2 = df[(as.numeric(as.character(df$origin)) >= 16) & (as.numeric(as.character(df$origin)) <= 40), ]
    ))
}

# Fitting ADLP class
fit3 <- adlp(
    components_lst = components,
    newdata = valid_data,
    partition_func = user_defined_partition
)

fit3
```

Comparing models through MSE
---



We can see that the ADLP ensembles perform better than all components on the 
in-sample and only slightly loses out to base model 1 on the out-of-sample data.

Note that this may also be due to model variance and we have not chosen to 
optimise the base models.

```{r}
show_mse <- function(data) {
    print("----------------------------")
    print("Base models 1, 2, 3")
    print(sum((predict(base_model1_full, data, type = "response") - data$claims)^2))
    print(sum((predict(base_model2_full, data, type = "response") - data$claims)^2))
    print(sum((predict(base_model3_full, data, type = "response") - data$claims)^2))
    
    print("ADLP ensembles 1, 2, 3")
    print(sum((predict(fit1, data)$ensemble_mu - data$claims)^2))
    print(sum((predict(fit2, data)$ensemble_mu - data$claims)^2))
    print(sum((predict(fit3, data)$ensemble_mu - data$claims)^2))
    print("----------------------------")
}

show_mse(train_data)
show_mse(valid_data)
show_mse(test_data)
```
